### 2019-10-31 README.Rmd
remove fungorum links in package, site temporarily down, rbuildignore a file
fix ipni broken link
Correct label link

	<td style="text-align:left;"><a href="http://www.ipni.org/link_to_ipni.html">link</a></td>

@@

	<td style="text-align:left;"><a href="http://www.indexfungorum.org/ixfwebservice/fungus.asmx">link</a></td>

@@

See the [newdatasource](https://github.com/ropensci/taxize/labels/newdatasource) tag in the issue tracker

>>>>

@@

@@

See the [datasources](https://github.com/ropensci/taxize/labels/datasources) tag in the issue tracker
